% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
% the margin option causes section ttextitles to appear to the left of body text
\textwidth=5.2in % increase textwidth to get smaller right margin
% \usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage[comma, sort&compress]{natbib}
\makeatletter
\renewenvironment{thebibliography}[1]
     {%\section*{\refname}% <--- outcommented
      \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
      \list{\@biblabel{\@arabic\c@enumiv}}%
           {\settowidth\labelwidth{\@biblabel{#1}}%
            \leftmargin\labelwidth
            \advance\leftmargin\labelsep
            \@openbib@code
            \usecounter{enumiv}%
            \let\p@enumiv\@empty
            \renewcommand\theenumiv{\@arabic\c@enumiv}}%
      \sloppy
      \clubpenalty4000
      \@clubpenalty \clubpenalty
      \widowpenalty4000%
      \sfcode`\.\@m}
     {\def\@noitemerr
       {\@latex@warning{Empty `thebibliography' environment}}%
      \endlist}
\makeatother
\begin{document}

\name{Tian Tian\\[14pt]} % the \\[12pt] adds a blank line after name


\address{ HCI D120 \\
          Vladimir-Prelog-Weg 1/5 \\
          ETH Z\"{u}rich, CH-8093, Z\"{u}rich, Switzerland \\
          +41-44-63-37330 \\
          Mail: tian.tian@chem.ethz.ch}
\address{{} \\  \\  \\
        }

\begin{resume}


\section{Education}

\textbf{PhD Candidate} \hfill October 2015-Current\\
Department of Chemistry and Applied Biosciences, ETH Z\"{u}rich

\textbf{M.Sc. of Chemistry}  \hfill August 2012-July 2015\\
Department of Chemistry, Tsinghua University

\textbf{B.Sc. of Chemical Biology}  \hfill August 2008-July 2012\\
Department of Chemistry, Tsinghua University

\textbf{Minor in Computer Technology and Application}  \hfill August 2010-July 2012\\
Department of Computer Science and Technology, Tsinghua University

\section{Research Experience}
\textbf{Doctoral Projects} \hfill 2015-Current\\
\textit{Supervisor}: Prof. Chih-Jen Shih (ETH Z\"{u}rich, Switzerland)\\
Fundamental Research on Graphene and Other Two-Dimensional Materials
\begin{itemize} \itemsep -2pt
  \item Modeling the penetration of an electric displacement field through graphene 2D electron gas.
  \item Modeling the wetting properties on charged graphene surface
  \item Graphene-gating based organic electronic devices
\end{itemize}

\textbf{Master Work} \hfill 2012-2015\\
\textit{Supervisor}: Prof. Guangtao Li (Tsinghua University, China)\\
 \textit{Thesis Title}: Research of Multi-functional Photonic Crystal Systems Based on Chemical Reaction
 \begin{itemize} \itemsep -2pt  % reduce space between textitems
 \item Maleimide-containing responsive polymer inverse opal and its application in assaying  of acetylcholinesterase
 \item Chemical and structural complexity in colloidal crystal beads using etching-reaction approach
 \item Multi-functional pattern formation in 3D photonic crystal film using alternative photolysis-reaction strategy
 \end{itemize}

\textbf{Laboratory Internship} \hfill Summer 2012\\
 \textit{Supervisor}: Prof. Bart Jan Ravoo (WWU M\"{u}nster, Germany)\\
 \textit{Research Topic}: Synthesis of Guest Molecules with Tri-Responsiveness in Cyclodextrin Vesicle Linking


\textbf{Bachelor Work} \hfill 2011-2012\\
\textit{Supervisor}: Prof. Guangtao Li (Tsinghua Universtity, China)\\
 \textit{Thesis Title}: Synthesis of Functional Main-Chain Bile Acid Polymer by Click Reaction
 \begin{itemize} \itemsep -2pt  % reduce space between textitems
 \item Synthesis of main-chain bile acid polymers using Cu-free click chemistry with improvement of stereo selectivity
 \item Supramolecular assembly of main-chain bile acid polymers
 \end{itemize}


\section{Research \\Interests}
              \begin{itemize}
                \item Computational simulation of interfacial properties.
                \item Two-dimensional materials
                \item Self assembly in varied scales
                \item Organic synthesis with    rational design
		          \end{itemize}




% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Academic Awards}
\begin{itemize}
   \item Teijin Academic Scholarship (first-class academic scholarship) \hfill October 2014
   \item Outstanding Graduate of Tsinghua University \hfill July 2012
   \item Tsinghua School Scholarship for elite students \hfill January 2012
   \item First-class National Scholarship \hfill November 2011
   \item Third-class Academic Scholarship \hfill November 2010
   \item Dingye Mailin Academic Scholarship \hfill November 2009
\end{itemize}

\section{Language Level}
\textbf{English} (IELTS score: 7.5, tested on November 2014)


\section{Publications}
\begin{enumerate}
  \item \textbf{Tian, T.}; Rice, P. Santos, E.J.; Shih, C.-J. \textit{Nano Lett.} \textbf{2016}, \textit{16}, 5044-5052.
  \item \textbf{Tian, T.}; Gao, N.; Gu, C.; Li, J.; Wang, H.; Lan, Y.; Yin, X.; Li, G.; \textit{ACS Appl. Mater. Interfaces} \textbf{2015}, \textit{7}, 19516-19525.
  \item \textbf{Tian, T.}; Li, X.; Cui, J.; Li, J.; Lan, Y.; Wang, C.; Zhang, M.; Wang, H.; Li, G. \textit{ACS Appl. Mater. Interfaces} \textbf{2014}, \textit{50}, 15456-15465.
  \item Wang, H.; Zhu, W.; Li, J.; \textbf{Tian, T.}; Lan, Y.; Gao, N.; Wang, C.; Zhang, M.; Faul, C. F.; Li, G. \textit{Chem. Sci.} \textbf{2015}, \textit{6}, 1910-1916.
  \item Zhang, M.; Yin, X.; \textbf{Tian, T.}; Liang, Y.; Li, W.; Lan, Y.; Li, J.; Zhou, M.; Ju, Y.; Li, G. \textit{Chem. Commun.} \textbf{2015}, \textit{51}, 10210-10213.
  \item Wang, C.; Shang, J.; Lan, Y.; \textbf{Tian, T.}; Wang, H.; Gu, J.-Y.; Liu, J. Z.; Wan L.-J.; Zhu, W.; Li, G. \textit{Adv. Funct. Mater.} \textbf{2015}, \textit{25}, 6009-6017.
  \item Li, W.; \textbf{Tian, T.}; Lan, Y.; Zhu, W.; Li, J.; Zhang, M.; Ju, Y.; Li, G. \textit{Polym. Chem.} \textbf{2014}, \textit{5}, 743-751.
  \item Wang, C.; Zhu, W.; Lan, Y.; Zhang, M.; \textbf{Tian, T.}; Wang, H.; Li, G. \textit{J. Phys. Chem. C} \textbf{2014}, \textit{118}, 10754-10763.
  \item Xu, D.; Zhu, W.; Wang, C.; \textbf{Tian, T.}; Cui, J.; Li, J.; Wang, H.; Li, G. \textit{Chem. Eur. J.} \textbf{2014}, \textit{20}, 16620-16625.
  \item Xu, D.; Zhu, W.; Wang, C.; \textbf{Tian, T.}; Li, J.; Lan, Y.; Zhang, G.; Zhang, D.; Li, G. \textit{Chem. Commun.} \textbf{2014}, \textit{50}, 14133-14136.
  \item Yang, H.; Li, X.; Lan, Y.; \textbf{Tian, T.}; Cui, J.; Zhu, T.; Shen, D.; Li, G. \textit{J. Mater. Chem. C} \textbf{2013}, \textit{1}, 6120-6128.
  \item Li, W.; \textbf{Tian, T.}; Zhu, W.; Cui, J.; Ju, Y.; Li, G. \textit{Polym. Chem.} \textbf{2013}, \textit{4}, 3057-3068.
  \item Zhu, T.; Xu, D.; Wu, Y.; Li, J.; Zhou, M.; \textbf{Tian, T.}; Jiang, Y.; Li, F.; Li, G. \textit{J. Mater. Chem. B} \textbf{2013}, \textit{1}, 6449-6458.
  \item Li, X.; Peng, L.; Cui, J.; Li, W.; Lin, C.; Xu, D.; \textbf{Tian, T.}; Zhang, G.; Zhang, D.; Li, G. \textit{Small} \textbf{2012}, \textit{8}, 612-618.


\end{enumerate}
\bibliographystyle{achemso}
\bibliography{cv}

\end{resume}
\end{document}
