\documentclass[11pt, a4paper]{cv}
% \usepackage{showframe}
% \usepackage{lua-visual-debug}

\renewcommand{\acvHeaderSocialSep}{\quad\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%-------------------------------------------------------------------------------

% \photo[rectangle,noedge,right]{./img/portrait.jpg}
\name{Tian}{Tian}
\position{
  PhD Candidate\\
  D-CHAB, ETH Z\"{u}rich
}
\address{
  Vladimir-Prelog Weg 1, HCI E120 \\ CH-8093, Z\"{u}rich, Switzerland}
\mobile{(+41) 446337330}

\email{tian.tian@chem.ethz.ch}

%-------------------------------------------------------------------------------
\begin{document}

\makeletterheader[L]{}

\makecvfooter
{}
{}
{}

\recipient
  {Prof. Dr. XXX}
  {Univ YY \\ Address \\ Country}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application }
% How the letter is opened
\letteropening{Dear Prof. LastName,}
% How the letter is closed
\letterclosing{Sincerely,}

\makelettertitle

\begin{cvletter}
  
  I am writing to inquire the possibility of a postdoctoral position
  in your research group. I recently defended my PhD and continue to
  work as a short-term researcher in the Institute of Chemical and
  Bioengineering, Department of Applied Chemistry and Biosciences, ETH
  Zürich. I am particularly interested in the research direction of
  XXX in your group, which I believe will YYYY.


  As shown in my curriculum vitae enclosed, I was mainly trained as
  experimental chemist specialized in material design and synthesis
  during my bachelor and master studies, during which time I gained
  understandings desire for theoretical studies and material
  simulations.  Driven by my enthusiasm about theoretical material
  simulations, I conducted my PhD thesis entitled “ZZZ” under the
  supervision of Prof. Chih-Jen Shih. My PhD studies combine both
  multiscale simulations and experimental demonstrations, to
  illucidate the complex interfacial phenomena of two-dimensional
  materials. Particular interests were focused on 1) electrostatic
  interaction through QC, and further use the multiscale model to ….




  Part II \& III left blank


  Several sentences for boasting myself….  If you foresee a
  possibility for a postdoctoral position based on my cover letter and
  curriculum vitae, I would greatly appreciate having further
  discussion about the research projects with you. There are also
  funding options from the SNSF early-postdoc Mobility project (link
  to website), which I would be enlighted to apply together with you
  before March 2020.


\end{cvletter}

\makeletterclosing




%-------------------------------------------------------------------------------
\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
