%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experiences}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
% ------------------------------------
\cventry
{Doctoral Projects (Supervisor: Prof.  Chih-Jen Shih)} % Degree
{ETH Z\"{u}rich} % Institution
{Switzerland} % Location
{Oct. 2015 - Jan. 2020 (Expected)} % Date(s)
{
  % 
  \begin{cvitems}
  \item Multiscale modeling of 2D materials interfaces
  \item Theoretical study of macroscopic phenomena on 2D materials
  \item Molecular epitaxy on 2D materials interfaces
  \item 2D material-based functional devices
  \end{cvitems}
}

% ---------------------------------------------------------
\cventry
{Research Internship (Supervisor: Prof.  Elton G. J. Santos)} %
{Queen's University Belfast} % Institution
{United Kindom} % Location
{Jun. 2012 - Sep. 2015} % Date(s)
{
  % 
  \begin{cvitems}
  \item \textit{Ab initio} study of the dielectric nature of 2D materials
  \item Electric screening in 2D van der Waals heterostructures
  \end{cvitems}
}

% ---------------------------------------
\cventry
{Master Thesis (Supervisor: Prof.  Guangtao Li)}
{Tsinghua University}
{China}
{Aug. 2012 - Jul. 2015}
{
  \begin{cvitems}
  \item Responsive polymer photonic crystal and for acetylcholinesterase assay
  \item Chemical and structural design in colloidal crystal microfluidic spheres using etching-reaction strategy
  \item Multi-functional patterned photonic crystal by alternative photolysis-reaction strategy
  \end{cvitems}
}

% --------------------------------------
\cventry
{Research Internship (Supervisor: Prof. Bart Jan Ravoo)} % Degree
{WWU M\"{u}nster} % Institution
{Germany} % Location
{Jul. 2012 - Aug. 2012} % Date(s)
{
  \begin{cvitems}
  \item Synthesis of host-guest complex with tri-responsiveness for
    cyclodextrin vesicle linking
  \end{cvitems}
}
% ---------------------------------------------------------

\cventry
{Bachelor Thesis (Supervisor: Prof.  Guangtao Li)} % Degree
{Tsinghua University} % Institution
{China} % Location
{Nov. 2011 - Jul. 2012} % Date(s)
{
  \begin{cvitems}
  \item Supramolecular assembly of main-chain bile acid polymers via copper-free click chemistry
  \end{cvitems}
}
\end{cventries}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../cv"
%%% End:
